Simulation study in rectangular domain

### 2024-04-19 Latex/main.tex
add new files due to changes in smoothSDE package

By integrating the velocity equation over time one gets the transition density of the location process.
\begin{equation}
	X(t+\Delta) \vert X(t)=x, V(t)=v \sim \mathcal{N}\left(x+\mu \Delta+A^{-1} \left( I_2-\exp(-A\Delta)\right)(v-\mu),Q(\Delta)\right)  
\end{equation}
Here, the covariance matrix $Q(\Delta)$ has an explicit form.

\[
	Q(\Delta)=\left( \Delta-2 \frac{\omega \sin(\omega \Delta)-\frac{1}{\tau} \cos(\omega \Delta)}{\frac{1}{\tau^2}+\omega^2 } \exp\left( -\frac{\Delta}{\tau} \right) +\frac{\tau}{2} \left( \frac{\omega^2-\frac{3}{\tau^2}}{\frac{1}{\tau^2}+\omega^2}-\exp\left( -\frac{2\Delta}{\tau}\right)\right) \right) I_2
\]
The position process is not markovian, but the whole process $(x(t), v(t))^\top$ is.
Both components of the location and velocity processes are independent.
and one can check that for $\omega=0$, the formulas match the ones of the  CTCRW model \cite{johnson_continuoustime_2008}. Figure~\ref{fig: sample RACVM} shows two samples of a RCVM along with the histograms of the empirical velocity norm and phase. Derivation of the formulas given in this paragraph is detailed in appendix~\ref{section: detailed RACVM computations}.\\

@@

 \[
 \omega(\theta,D_{shore})=\frac{\omega_0}{2}\left(\tanh(\lambda(\theta+\frac{\pi}{2}))+\tanh(\lambda(\theta-\frac{\pi}{2})))\right)\times c(D_{shore})
 \]
 for some $\omega_0 \in \R$, $\lambda>0$

@@

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[scale=0.4]{images/simulation study/samples_rect_hf_ne_omega.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[scale=0.4]{images/simulation study/samples_rect_hf_e_omega.png}
		\caption{}
	\end{subfigure}
	\caption{Samples of the CRCVM. x and y axis are in metres and initial positions are indicated by a red cross (a)-(b) Two samples of time step $h=1$ min (high frequency) with respective measurement errors standard deviation $\sigma_{obs}=3$ m and $\sigma_{obs}=30$ m.}
	\label{fig: samples_rect_CRCVM}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[scale=0.5]{images/simulation study/samples_fjords_hf_ne_omega.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[scale=0.5]{images/simulation study/samples_fjords_hf_e_omega.png}
		\caption{}
	\end{subfigure}
	\caption{Samples of the CRCVM. x and y axis are in metres and initial positions are indicated by a red cross. (a)-(b) Two samples of time step $h=1$ min (high frequency) with respective measurement errors standard deviation $\sigma_{obs}=3$ m and $\sigma_{obs}=30$ m.}
	\label{fig: samples_fjords_CRCVM}
\end{figure}

\begin{comment}

To assess whether the CRCVM can describe a tendecy to move along the boundary, $\tau$ was then also expressed as a smooth function of $D_{shore}$ and $\Theta$.
\begin{align*}	
	\tau(\theta,D_{shore})&=(1-c(D_{shore}))\times \tau_0 +c(D_{shore}) \times   \\
	&+\left(\Delta_0+(\tau_0-\Delta_0)\exp\left(\frac{-\theta^2}{\pi^2}\right)+
	(\tau_1-\Delta_0)\exp\left(-\lambda_{\tau}\left(\theta-\frac{\pi}{2}\right)^2\right)+(\tau_2-\Delta_0)\exp\left(-\lambda_{\tau}\left(\theta+\frac{\pi}{2}\right)^2\right)\right)
\end{align*}
for some $0<\Delta_0<\tau_0<\tau_1,\tau_2$ and $\lambda_{\tau}>0$.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\linewidth]{"images/simulation study/true_tau"}
	\caption{$\tau$ (unit: $h$) as a smoth function of $\Theta$ and $D_{shore}$. Values of $D_{shore}$ are in $km$ and values of $\Theta$ are in $rad$}
	\label{fig:truetau}
\end{figure}

\end{comment}

>>>>

By integrating the velocity equation over time one gets the following distribution for the location process :
\begin{equation}
	X(t+\Delta) \vert X(t)=x, V(t)=v \sim \mathcal{N}\left(x+\mu \Delta+A^{-1} \left( I_2-\exp(-A\Delta)\right)(v-\mu),Q(\Delta)\right)  
\end{equation}
Here, the covariance matrix $Q(\Delta)$ has an explicit form.

\[
	Q(\Delta)=\left( \Delta-2 \frac{\omega \sin(\omega \Delta)-\frac{1}{\tau} \cos(\omega \Delta)}{\frac{1}{\tau^2}+\omega^2 } \exp\left( -\frac{\Delta}{\tau} \right) +\frac{\tau}{2} \left( \frac{\omega^2-\frac{3}{\tau^2}}{\frac{1}{\tau^2}+\omega^2}-\exp\left( -\frac{2\Delta}{\tau}\right)\right) \right) I_2
\]
The location process is not markovian, but the whole process $(x(t), v(t))^\top$ is.
Both components of the location and velocity processes are independent.
and one can check that for $\omega=0$, the formulas match the ones of the  CTCRW model \cite{johnson_continuoustime_2008}. Figure~\ref{fig: sample RACVM} shows two samples of a RCVM along with the histograms of the empirical velocity norm and phase. Derivation of the formulas given in this paragraph is detailed in appendix~\ref{section: detailed RACVM computations}.\\

@@

 \[
 \omega(\theta,D_{shore})=\frac{\omega_0}{2}\left(\tanh(\lambda(\theta+\theta^{*}))+\tanh(\lambda(\theta-\theta^{*})))\right)\times c(D_{shore})
 \]
 for some $\omega_0 \in \R$, $\lambda>0$, $\theta^* \in [0,2\pi]$.

@@

 \begin{figure}[H]
 	\centering
 	\begin{subfigure}{0.48\textwidth}
 		\centering
 		\includegraphics[scale=0.4]{images/simulation study/samples_rect_hf_ne_omega.png}
 		\caption{}
 	\end{subfigure}
 	\begin{subfigure}{0.48\textwidth}
 		\centering
 		\includegraphics[scale=0.4]{images/simulation study/samples_rect_hf_e_omega.png}
 		\caption{}
 	\end{subfigure}
 	\caption{Samples of the CRCVM in a rectangular domain. x and y axis are in metres and initial positions are indicated by a red cross (a)-(b) Two samples of time step $h=1$ min (high frequency) with respective measurement errors standard deviation $\sigma_{obs}=3$ m and $\sigma_{obs}=30$ m.}
 	\label{fig: samples_rect_CRCVM}
 \end{figure}

 \begin{figure}[H]
 	\centering
 	\begin{subfigure}{0.48\textwidth}
 		\centering
 		\includegraphics[scale=0.5]{images/simulation study/samples_fjords_hf_ne_omega.png}
 		\caption{}
 	\end{subfigure}
 	\begin{subfigure}{0.48\textwidth}
 		\centering
 		\includegraphics[scale=0.5]{images/simulation study/samples_fjords_hf_e_omega.png}
 		\caption{}
 	\end{subfigure}
 	\caption{Samples of the CRCVM in Scoresby Sound coastline geometry. x and y axis are in metres and initial positions are indicated by a red cross. (a)-(b) Two samples of time step $h=1$ min (high frequency) with respective measurement errors standard deviation $\sigma_{obs}=3$ m and $\sigma_{obs}=30$ m.}
 	\label{fig: samples_fjords_CRCVM}
 \end{figure}

@@

### 2024-04-19 R/simulation_study/simulation_study_rect.Rmd
add new files due to changes in smoothSDE package

ggsave("all_batches_coeffs_crcvm_rect_hf_ne1.png",plot=p,path="crcvm_rect_hf_ne1")

@@

ggsave("all_batches_coeffs_crcvm_rect_hf_ne2.png",plot=p,width=10,height=5,path="crcvm_rect_hf_ne2")

@@

ggsave("all_batches_coeffs_crcvm_rect_hf_e1.png",plot=p,width=10,height=5,path="crcvm_rect_hf_e1")

ggplotly(p)

@@

ggsave("all_batches_coeffs_crcvm_rect_hf_e2.png",plot=p,width=10,height=5,path="crcvm_rect_hf_e2")
```

>>>>

p=ggplotly(p)
saveWidget(p, file ="crcvm_rect_hf_ne1/all_batches_coeffs_crcvm_rect_hf_ne1.png")

@@

p=ggplotly(p)
saveWidget(p, file ="crcvm_rect_hf_ne2/all_batches_coeffs_crcvm_rect_hf_ne2.png")

@@

p=ggplotly(p)
saveWidget(p, file ="crcvm_rect_hf_e1/all_batches_coeffs_crcvm_rect_hf_e1.png")

@@

p=ggplotly(p)
saveWidget(p, file ="crcvm_rect_hf_e2/all_batches_coeffs_crcvm_rect_hf_e2.png")
```
